Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Clean up proof of Theorem 2

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:7} to get
\begin{align*}
  \hat\tau(h)^* - &\Delta_h^{**} - \tau^*
  = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}_h - \tau^{**}) \\
  &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
   + h^2 (\hat\mu_-^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
   - h^2 (\hat\mu_+^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
  &= \Omega^{+}(b)' \epb_{+}^{*} - \Omega^{-}(b)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_b^{+}}^{*})'$ and
$\Omega^{+}_b$ is an $M_b^{+}$-dimensional vector with $i$th element
$\Omega_{1i}^{+}(b) - \Omega_{2i}^{+}(b)$, which are defined as
\begin{align*}
  \Omega_{1i}^{+}(b) &=
  (1\quad 0)
  \Big(\ssum{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
    r_1(X_{m^+_i} / h) \1\{h > X_{m_i} \geq 0\}
\intertext{and}
  \Omega_{2i}^{+}(b) &= (0\quad 0 \quad h^2)
  \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m^+_i} / b).
\end{align*}
Here $r_p(x) = (1, x, x^2,\dots,x^{p})'$ and $m^+_i$ is the subsequence of
$1,2,\dots$ such that $0 \leq X_{m_i} < b$. The definitions of
$\epb_{-}^{*}$ and $\Omega^-(b)$ have the same definitions as
$\epb_{+}^{*}$ and $\Omega^+(b)$ after making the obvious
substitutions of ``$-$'' for ``$+$.''

Given~\eqref{eq:7}, it suffices to prove that
\begin{gather}
  \label{eq:8}
  \rho(V^{-1/2}(h) \Omega^{+}(b)'\epb_{+}^{*},
    V^{-1/2}(h)\Omega^{+}(b)'\epb_{+}) \to^p 0
  \intertext{and}
  \label{eq:9}
  \rho(V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}^{*},
    V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}) \to^p 0
\end{gather}
with $\epb_+$ an i.i.d. random vector of length $M_b^+$, the $i$th
element of which is distributed as
\[
  \varepsilon_{i,+} =^d
  \begin{cases}
    Y_{m_1^+} - \E(Y_{m_1^+} \mid X_{m_1^+})
    & \text{with probability\ } 1/M_{b}^+ \\
    \vdots \\
    Y_{m_{M_b^+}^+} - \E(Y_{m_{M_b^+}^+} \mid X_{m_{M_b^+}^+})
    & \text{with probability\ } 1/M_{b}^+,
  \end{cases}
\]
$\epb_-$ the corresponding quantity after replacing ``+'' with ``--,'' and
$\rho$ the Mallows metric \citep{bickel1981}.\footnote{%
  For two random vectors $u$ and $v$ with finite 2nd moments, $\rho(u, v)$
  is defined as
  \begin{equation*}
    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
  \end{equation*}}

We will only prove~\eqref{eq:8} since the proof of~\eqref{eq:9} is
identical. By Theorem 2.1 of \cite{freedman1981}, we have
\begin{align*}
  \rho(V^{-1/2}(h) \Omega^{+}(b)'\epb_{+}^{*}, V^{-1/2}(h)&\Omega^{+}(b)'\epb_{+}) \\
  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
    \tr(V^{-1/2}(h) \Omega^{+}(b)' \Omega^{+}(b)V^{-1/2}(h)) \\
  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
\end{align*}
the second line holding as a consequence of CCT's Lemma SA1. So it suffices
to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
$\dot{\varepsilon}_i$ be an i.i.d. sequence randomly drawn from $\epb_+$
with replacement and let
$\bar{\varepsilon} = (1/M_b^{+}) \osum{i}{b} \dot{\varepsilon}_i$. Then,
using the same arguments as \cite{freedman1981}, we have the upper bound
\begin{equation*}
  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
  \leq
  \bar\varepsilon^2 +
  (2/M_{b}^+) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
  + \rho(\dot\varepsilon_1, \varepsilon_{+,1}).
\end{equation*}
But $\bar\varepsilon^2 \to^p 0$ by the LLN,
\[
  (1/M_{b}^+) \osum[+]{i}{b}
  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
\]
by CCT's Lemma SA1, and
$\rho(\dot\varepsilon_1, \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
\cite{bickel1981}.\qed

>>>>

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:7} to get
\begin{align*}
  \hat\tau(h)^* - &\Delta^{**}(h,b) - \tau^*
  = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}(h) - \tau^{**}) \\
  &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
   + h^2 (\hat\mu_-^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
   - h^2 (\hat\mu_+^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
$\Omega_+(h,b)$ is an $M_b^{+}$-dimensional vector with $i$th element
$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
\begin{align*}
  \Omega_{+,1i}(h,b) &=
  (1\quad 0)
  \Big(\ssum{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
\intertext{and}
  \Omega_{2i}^{+}(h,b) &= (0\quad 0 \quad h^2)
  \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m_+(b,i)} / b).
\end{align*}
The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same definitions as
$\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the obvious substitutions of
``$-$'' for ``$+$.''

Given~\eqref{eq:7}, it suffices to prove that
\begin{gather}
  \label{eq:8}
  \rho(V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}^{*},
    V^{-1/2}(h,b)\Omega_+(h,b)'\epb_{+}) \to^p 0
  \intertext{and}
  \label{eq:9}
  \rho(V^{-1/2}(h,b)\Omega^{-}(b)'\epb_{-}^{*},
    V^{-1/2}(h,b)\Omega^{-}(b)'\epb_{-}) \to^p 0
\end{gather}
with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th element of
which is distributed as
\[
  \varepsilon_{i,+} =^d
  \begin{cases}
    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
    & \text{with probability\ } 1/M_+(b) \\
    \vdots \\
    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(1,b)})
    & \text{with probability\ } 1/M_+(b),
  \end{cases}
\]
$\epb_-$ the corresponding quantity after replacing ``+'' with ``--,'' and
$\rho$ the Mallows metric \citep{bickel1981}.\footnote{%
  For two random vectors $u$ and $v$ with finite 2nd moments, $\rho(u, v)$
  is defined as
  \begin{equation*}
    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
  \end{equation*}}

We will only prove~\eqref{eq:8} since the proof of~\eqref{eq:9} is
identical. By Theorem 2.1 of \cite{freedman1981}, we have
\begin{align*}
  \rho(V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}^{*},\
  &V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}) \\
  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
    \tr(V^{-1/2}(h,b) \Omega_+(h,b)' \Omega_+(h,b)V^{-1/2}(h,b)) \\
  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
\end{align*}
the second line holding as a consequence of CCT's Lemma SA1. So it suffices
to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
$\dot{\varepsilon}_i$ be an i.i.d. sequence randomly drawn from $\epb_+$
with replacement and let
$\bar{\varepsilon} = (1/M_+(b)) \osum[+]{i}{b} \dot{\varepsilon}_i$. Then,
using the same arguments as \cite{freedman1981}, we have the upper bound
\begin{equation*}
  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
  \leq
  \bar\varepsilon^2 +
  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
  + \rho(\dot\varepsilon_1, \varepsilon_{+,1}).
\end{equation*}
But $\bar\varepsilon^2 \to^p 0$ by the LLN,
\[
  (1/M_{b}^+) \osum[+]{i}{b}
  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
\]
by CCT's Lemma SA1, and
$\rho(\dot\varepsilon_1, \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
\cite{bickel1981}.\qed
